Supplementary material for\\ A Benchmark of Named Entity Recognition Approaches in Historical Documents\\ Application to 19$^{th}$ Century French Directories

### 2022-01-20 src-latex/parts/20-related-work.tex
Conclusion

Based on those works, we chose to test three OCR systems, namely, Tesseract, Pero OCR, and Kraken. We also adopt two deep-learning-based French language models, available in packaged software libraries, already trained for the NER task and that we can adapt to the domain of historical directories: SpaCy NLP pipelines and CamemBERT.
\Cref{fig.pipeline} depicts the evaluation protocol used to assess the combined performance of these OCR and NER systems.

@@

\textbf{CamemBERT}
Language model based on \textit{Transformers} \cite{vaswani2017attention}, like BERT \cite{devlin2018bert}, have become a new paradigm for NER\cite{li2020}. 
The learned embeddings can be used as distributed representations for input instead of traditional embeddings like Google Word2Vec, and they can be further fine-tuned for NER by adding an additional output layer. 
They can also be pre-trained in an unsupervised way on historical texts for domain adaptation.
CamemBERT \cite{martin-etal-2020-camembert}, is a well-known French language model derived from BERT, of which there are already trained versions for the NER task on the Hugging Face library.

>>>>

Based on those works, we chose to test three OCR systems, namely, Tesseract, PERO OCR, and Kraken. We also adopt two deep-learning-based French language models, available in packaged software libraries, already trained for the NER task and that we can adapt to the domain of historical directories: SpaCy NLP pipelines and CamemBERT.
\Cref{fig.pipeline} depicts the evaluation protocol used to assess the combined performance of these OCR and NER systems.

@@

\textbf{CamemBERT}
Language model based on \textit{Transformers} \cite{vaswani2017attention}, like BERT \cite{devlin2018bert}, have become a new paradigm for NER\cite{li2020}. 
The learned embeddings can be used as distributed representations for input instead of traditional embeddings like Google Word2Vec, and they can be further fine-tuned for NER by adding an additional output layer. 
They can also be pre-trained in an unsupervised way on historical texts for domain adaptation.
CamemBERT \cite{martin-etal-2020-camembert}, is a well-known French language model derived from BERT, of which there are already trained versions for the NER task on the Huggingface library.

### 2022-01-20 src-latex/parts/50-ner-xp1-training-set-size-and-pretraining.tex
Conclusion

% !TeX root = ../main-paper.tex
\section{Experiment 1: NER sensibility to the number of training examples}
\label{sec:ner-xp1}
The constitution of annotated datasets to train a NER model is a critical preliminary step.
Often done manually, possibly with bootstrapped annotations, this task is tedious, time-consuming, and error-prone.
The ability of a model to perform well even with a few training examples is a practical criterion to consider.
In this first experiment, we investigate the NER performance of SpaCy and CamemBERT when fine-tuned with an increasing number of training examples.

@@

\begin{figure}[ht!]
	   \center{\includegraphics[width=\textwidth]
	       {figs/eval-ner-exp1.pdf}}
	  \caption{\label{fig:f1-vs-trainsize} Metrics measured on the fine-tuned models CmBERT, CmBERT+ptrn and SpaCy NER in experiment 1 for 8 training sets of increasing sizes. Precision and recall values are available in the appendix.}
\end{figure}

>>>>

% !TeX root = ../main-paper.tex
\section{NER sensibility to the number of training examples}
\label{sec:ner-xp1}
The constitution of annotated datasets to train a NER model is a critical preliminary step.
Often done manually, possibly with bootstrapped annotations, this task is tedious, time-consuming, and error-prone.
The ability of a model to perform well even with a few training examples is a practical criterion to consider.
In this first experiment, we investigate the NER performance of SpaCy and CamemBERT when fine-tuned with an increasing number of training examples.

@@

\begin{figure}[ht!]
	   \center{\includegraphics[width=\textwidth]
	       {figs/eval-ner-exp1.pdf}}
	  \caption{\label{fig:f1-vs-trainsize} Metrics measured on the fine-tuned models CmBERT, CmBERT+ptrn and SpaCy NER for 8 training sets of increasing sizes. Precision and recall values are available in the appendix.}
\end{figure}
